%    Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa


\begin{document}

%----------------------------------------------------------------------------------------
%   ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{} 

%----------------------------------------------------------------------------------------
%   YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf James Mueller \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
2601 Ridgefield Rd \\ Columbia MO, 65203 \\ (573) 881-2018 % Your address and phone number
\end{center} 
\vfill

\signature{James Mueller} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%   LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Riot Games,} 

I attended a talk at Strange Loop in Saint Louis by one of your engineers working on the League of Legends chat system, and because of that talk I am interested in working as a developer with you at either your Santa Monica or Saint Louis office. 

You service millions of concurrent users daily, and that brings with it a lot of really cool scaling issues that I'd love to work with. Where I work I love taking processes that were written years ago and making them fast and reliable. There are systems that are now a thousand times faster because we used modern database access techniques, mutlithreaded the processing and started using rabbit messages to write the output to keep it non-blocking. I'm sure that Riot has less low hanging fruit that can be optimized like that, but I'd like to apply what I've learned to a modern company with with talented engineers that can help push me. 

I also work as a full stack engineer, so I've modified network rules, written automation and deployment code, built web servers in Java and Groovy and written front end HTML, Javascript and CSS. I'm not against doing any of that as long as I'm working in a team of talented engineers.
 
I'll also say that I'm a gamer and I think it would be really cool to be able to say that I work at Riot Games and I help make League of Legends possible.

\closing{Thank you for your time,}



%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
 b = 100 - a

